The shape of kelp: environmental influences on kelp morphology

### 2018-10-03 chapter_2.Rmd
updated outputs and house cleaning for chapter 2

Kelps are sessile species and have to adapt to local environmental conditions in order to persist and survive. The resilence of kelps is evident through their distribution, which spans a range of environmental conditions that vary spatially and temporarly. Wave exposure and temperature are regarded as important environmental drivers with regards to macroalgae, and play a role in the growth, reproduction, and survival of kelp species. Wave exposure is recognised as the main cause of kelp mortality, which may manifest itself through dislodgment of individuals or breakage of important morphological structures. These mechanisms usually occur during times of high wave energy or pulse disturbance events, such as storms. Kelps are able to reduce the probablity of dislodgment or breakage through morphological adaptation, which may involve several strategies. Kelps can either reduce drag, increase attachment strength or increase flexibility in order to survive high wave energy environments.

>>>>

Kelps are sessile species and have to adapt to local environmental conditions in order to persist and survive. The resilience of kelps is evident through their distribution, which spans a range of environmental conditions that vary spatially and temporally. Wave exposure and temperature are regarded as important environmental drivers with regards to macroalgae, and play a role in the growth, reproduction, and survival of kelp species. Wave exposure is recognised as the main cause of kelp mortality, which may manifest itself through dislodgment of individuals or breakage of important morphological structures. These mechanisms usually occur during times of high wave energy or pulse disturbance events, such as storms. Kelps are able to reduce the probability of dislodgment or breakage through morphological adaptation, which may involve several strategies. Kelps can either reduce drag, increase attachment strength or increase flexibility in order to survive high wave energy environments.
